Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-08-09 paper/ms.tex
Correct caption

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ and \bizarreone,
    normalized to \elem{H} (top) and \elem{Fe} (bottom).
    Lines are drawn for each star only to guide the eye.
    \bizarreone\ is enhanced in \elem{Fe} by $\approx 0.2$~dex relative to
    \sunanalog\ along with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca},
    \elem{Ti}, \elem{V}, \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C},
    \elem{N}, \elem{O}, \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.9\linewidth]{abundances.pdf}
  \caption{Abundances of the comoving pair, \sunanalog\ (blue) and \bizarreone\
    (red). Lines are drawn for each star only to guide the eye. \bizarreone\ is
    enhanced in \elem{Fe} by $\approx 0.2$~dex relative to \sunanalog\ along
    with \elem{Mg}, \elem{Al}, \elem{Si}, \elem{Ca}, \elem{Ti}, \elem{V},
    \elem{Cr}, \elem{Ni}, \elem{Y} yet not in \elem{C}, \elem{N}, \elem{O},
    \elem{Na}, and \elem{Mn}.
  }
  \label{fig:abundances}
\end{figure}
